EEOB563 -- Assignment #5

### 2019-03-13 assignments/5/Assignment_5.Rmd
Rendered Assignment 5 without last part

@@

```
Raxml:  -54568.308901
FastMe: -54674.432495
```
![Tanglegram made with Dendroscope](3/Tanglegram.png)

@@

````
model_codons:
  GTR+G+FO, COBX=1-4482/3

@@

![Tanglegram made with Dendroscope](4/Genes_vs_3_raxml.png)

## 5
Unfortunately I can't do this part right now because HPC is having problems with slurm or something (I copied you on an email about this). I will resubmit this assignment including this part when it's fixed.

>>>>

---
title: 'EEOB563 -- Assignment #5'
author: "Dennis Psaroudakis"
date: "March 12th 2019"
output:
  pdf_document:
    dev: pdf
    latex_engine: lualatex
    md_extensions: +link_attributes+multiline_tables
    pandoc_args: --listings
    template: ../template.tex
mainfontoptions: Numbers=OldStyle
monofont: Linux Libertine Mono O
mainfont: Linux Libertine O
papersize: letter
sansfont: Linux Biolinum O
language: en-US
titlepage: true
...

@@

```
Raxml:  -54568.308901
FastMe: -54674.432495
```
![Tanglegram made with Dendroscope (zoom in)](3/Tanglegram.png)

\clearpage

@@

```
model_codons:
  GTR+G+FO, COBX=1-4482/3

@@

![Tanglegram made with Dendroscope (zoom in)](4/Genes_vs_3_raxml.png)

\clearpage

## 5
I had problems with slurm so I couldn't start it until Tuesday evening, so it's still running. I will resubmit this assignment tomorrow with part 5 when it is done. I am expecting a runtime of $\ge$ 10 hours from what the others have told me, I don't remember the runtimes from the lab anymore.
This is my slurm script:

```bash
#!/bin/bash

#SBATCH --time=10:30:00   # walltime limit (HH:MM:SS)
#SBATCH --nodes=1   # number of nodes
#SBATCH --ntasks-per-node=16   # 16 processor core(s) per node 
#SBATCH --job-name="5.5_assignment"
#SBATCH --mail-user=dpsaroud@iastate.edu   # email address
#SBATCH --mail-type=BEGIN
#SBATCH --mail-type=END
#SBATCH --mail-type=FAIL

# LOAD MODULES, INSERT CODE, AND RUN YOUR PROGRAMS HERE#!/bin/bash
cd /home/dpsaroud/EEOB563/assignments/5/5

/home/dpsaroud/bin/raxml-ng --all --msa ../alignment.phy --model GTR+G --seed 12 --threads 16 --bs-metric fbp --bs-trees 1000
```
